---
title: "Druggies"
author: "Breawna Diefenderfer"
date: "December 5, 2018"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
Female <- filter(abac,sex=="F")
Male <- filter(abac, sex=="M")
Druggies <- filter(abac, Ivdrug=="user")
Sexualorientation <- filter(abac, LBGT=="yes")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. In this report I will analyze the effectiveness of the abacavirinol drug, further refered to as "abac," in variable groups in order to see if any factors effect the drug. The groups on consideration are gender, intravenous(IV) drug use, and sexual orientation.
In this RMD file the data on IV drug users "Druggies" is reviewed.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
This report will look at graphs of the data in which the desired groups are seperated and classified by infection and drug type (real or placebo). In addition this report will compare the numeric precentages of infection by placebo or drug takers. It will compare p-values of the fisher test and chi-squared test to decide if the null hypothesis, the drug is less effective than the placebo, is rejected.
  
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
    
###Druggies data
```{r}
results1 <- xtabs(~infected+treatment, data = Druggies)
barchartGC(results1, type = "percent")
```
  
Of those who did not aquire AIDS those taking the placebo had a higher percentage than those taking the abac drug. Of the people who got AIDS more were taking the placebo than those who were on the drug, this indicates the drug is in fact preventing AIDS. This graph has a lower infection rate of those taking the drug than the placebo; this suggests the abac drug may work better on IV drug users than other groups.
## Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
###Druggies data
```{r}
colPerc(results1)
rowPerc(results1)
```
  Taking into account only those using IVdrug ("Druggies"): 3.17% of those taking the abac drug were infected and of those taking the placebo 7.4% became infected.
  ## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
###Druggies data
```{r}
chisqtestGC(results1, graph = TRUE)
```
  
  The low p-value, 0.0227, causes us to reject the null hypothesis.
  
```{r}
fisher.test(results1)
```
  The low p-value, 0.01929, causes us to reject the null hypothesis.
Because we reject the null hypothesis of both the fisher and chisquare test. We determine there is a positive correlation in the results of infection between those taking the placebo and those who do not.
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
In the trial taking into account only Druggies, the results proved that those taking the abac drug had lower AIDs infection rates than those taking the placebo. As shown in the bar chart and precentage tables only 3.17% of those taking the drug contracted AIDS. In both the fisher test and chi-squared test the null hypothesis is rejected, this means that the placebo does not have a greater affect on a patients health. The abac drug should be given to druggies as an AIDs prevention drug.